\begin{module}{G}{Geometry of Linear Maps}

\input{modules/6-G/standards.tex}
\input{modules/6-G/readiness/outcomes.tex}
\input{modules/6-G/readiness/resources.tex}



\CatchFileDef{\activities}{modules/6-G/activities.tex}

\newModuleSection
\begin{goals}
Today we will beign learning how linear transformations affect areas.
\end{goals}
\includeActivities{1}{14}{\activities}
\begin{summary}
Today we defined the \term{determinant}, which measures how linear transformations scale areas.
\end{summary}

\newModuleSection
\begin{goals}
Today we will learn how row operations affect determinants (Standard G1) and how to compute determinants (Standard G2).
\end{goals}
\includeActivities{15}{33}{\activities}
\begin{summary}
Today we learned how row operations affect determinants (Standard G1) and how to compute determinants (Standard G2).
\end{summary}

\newModuleSection
\begin{goals}
Today we will continue practicing computing determinants (Standard G2).
\end{goals}
\includeActivities{34}{40}{\activities}
\begin{summary}
Today we continued practicing computing determinants (Standard G2).
\end{summary}

\newModuleSection
\begin{goals}
Today we will learn how to compute \term{eigenvalues} and \term{eigenvectors} (standards G3 and G4).
\end{goals}
\includeActivities{41}{49}{\activities}
\begin{summary}
Today we learned how to compute \term{eigenvalues} and \term{eigenvectors} (standards G3 and G4).
\vfill
Next class we will practice computing eigenvectors more.
\end{summary}

\newModuleSection
\begin{goals}
Today we will practice computing eigenvectors more.
\end{goals}
\includeActivities{50}{54}{\activities}
\begin{summary}
Today we practiced computing eigenvectors more.
\end{summary}


\end{module}
