


\begin{applicationActivities}



\begin{definition}
  A subset of a vector space is called a \term{subspace} if it is
  itself a vector space.
\end{definition}



\begin{remark}
  To prove that a subset \(S\) is a subspace of a vectorspace \(V\), you need only verify that the operations on \(V\) restrict to the subset \(S\); that is you must check two things:

  \begin{itemize}
  \item The set is \textbf{closed under addition}: i.e. for any \(\vec{x},\vec{y} \in S\), \(\vec{x}+\vec{y}\) is also in \(S\).
  \item The set is \textbf{closed under scalar multiplication}: i.e. for any \(\vec{x} \in S\) and scalar \(c \in \IR\), the product \(c\vec{x}\) is also in \(S\).
\end{itemize}
\end{remark}

\begin{activity}{15}
Let \(S=\setBuilder{\begin{bmatrix} x \\ y \\ z \end{bmatrix}}{ x+2y+z=0}\).  

\begin{subactivity}
Let \(\vec{v}=\begin{bmatrix} x_1 \\ y_1 \\ z_1 \end{bmatrix}\) and \(\vec{w} = \begin{bmatrix} x_2 \\ y_2 \\ z_2 \end{bmatrix} \).  Show that if \(\vec{v}, \vec{w} \in S\), then \(\vec{v}+\vec{w} \in S\) as well.
\end{subactivity}
\begin{subactivity}
Let \(\vec{v}=\begin{bmatrix} x_1 \\ y_1 \\ z_1 \end{bmatrix}\) and let $c \in \IR$.  Show that if \(\vec{v} \in S\), then \(c\vec{v} \in S\) as well.
\end{subactivity}

Therefore \(S\) is a subspace of \(\IR^3\)
\end{activity}

\begin{activity}{10}
  Prove that \(P=\setBuilder{ax^2+b}{a,b \in \IR}\) is a subspace
  of the vector space of all degree-two polynomials by showing it is closed under addition and scalar multiplication.
\end{activity}

\begin{activity}{10}
Let \(P\) be the set of all positive real numbers.  Determine if \(P\) is a subspace of \(\IR\) or not.
\end{activity}

\begin{remark}
Since \(0\) is a scalar and \(0\vec{v}=\vec{0}\) for any vector \(\vec{v}\), a set that is closed under scalar multiplication must contain the zero vector.
\ \\
\ \\
Therefore, if a set does {\bf not} contain the zero vector, it is {\bf not} a subspace.
\end{remark}

\begin{activity}{10}
  Consider the subset of \(\IR^2\) where at least one coordinate of
  each vector is \(0\).
  \begin{center}
    \begin{tikzpicture}[scale=0.25]
    \draw[thin,gray,<->] (-5,0) -- (5,0);
    \draw[thin,gray,<->] (0,-5) -- (0,5);
    \draw[thick,blue] (-4.8,0) -- (4.8,0);
    \draw[thick,blue] (0,-4.8) -- (0,4.8);
    \end{tikzpicture}
  \end{center}

Determine if this is a subspace of \(\IR^2\) or not.

  \begin{instructorNote}
   A quick picture easily illustrates that this is not a subspace. 
  \end{instructorNote}
\end{activity}



\begin{activity}{5}
  Show that the set of \(2\times 2\) matrices
  \[S=
    \left\{
    \begin{bmatrix}a&b\\-b&-a\end{bmatrix} :
    a,b\text{ are real numbers}
    \right\}
  \]
  is a subspace of \(\IR^{2\times 2}\) .
\end{activity}

\begin{activity}{10}
Let \(W\) be a subspace of a vector space \(V\).  How are \(\vspan W\) and \(W\) related?
\begin{enumerate}[(a)]
\item \(\vspan W\) is bigger than \(W\)
\item \(\vspan W\) is the same as \(W\)
\item \(\vspan W\) is smaller than \(W\)
\end{enumerate}
\end{activity}

\begin{fact}
  If \(S\) is a subset of a vector space \(V\), then
  \(\vspan S\) is a subspace of \(V\).  In fact, it is the smallest subspace of \(V\) containing \(S\).
\end{fact}

\end{applicationActivities}
