\begin{module}{A}{Algebraic properties of linear maps}

\input{modules/4-A/standards.tex}
\input{modules/4-A/readiness/outcomes.tex}


\CatchFileDef{\activities}{modules/4-A/activities.tex}

\newModuleSection
\begin{goals}
Today we will learn about \term{linear transformations} (Standard A1).
\end{goals}
\includeActivities{1}{11}{\activities}
\begin{summary}
Today we learned how to determine if a map between Eucliden spaces is a  \term{linear transformation} or not (Standard A1).
\end{summary}

\newModuleSection
\begin{goals}
Today we will learn how to use matrices to summarize linear maps (Standard A2).
\end{goals}
\includeActivities{12}{22}{\activities}
\begin{summary}
Today we learned how to use matrices to summarize linear maps (Standard A2).
\end{summary}

\newModuleSection
\begin{goals}
Today we will learn about an important subspace called the \term{kernel} of a linear transformation (Standard A3).
\end{goals}
\includeActivities{23}{28}{\activities}
\begin{summary}
Today we learned about the \term{kernel} of a linear transformation (Standard A3).
\end{summary}

\newModuleSection
\begin{goals}
Today we will learn about an important subspace called the \term{image} of a linear transformation (Standard A3).
\end{goals}
\includeActivities{29}{35}{\activities}
\begin{summary}
Today we learned about the \term{image} of a linear transformation (Standard A3).
\end{summary}

\newModuleSection
\begin{goals}
Today we will learn about \term{injective} and \term{surjective} linear maps (Standard A4).
\end{goals}
\includeActivities{36}{51}{\activities}
\begin{summary}
Today we learned about \term{injective} and \term{surjective} linear maps (Standard A4).
\end{summary}

\newModuleSection
\begin{goals}
Today we will learn about \term{bijective} linear maps. This will be needed when we learn about \term{invertible matrices} (Standard M2).
\end{goals}
\includeActivities{52}{64}{\activities}
\begin{summary}
Today we learned about \term{bijective} linear maps. This will be important when we learn about \term{invertible matrices} (Standard M2) in the next module.
\end{summary}


\end{module}
