\begin{module}{E}{Solving Systems of Linear Equations}

\input{modules/1-E/standards.tex}
\input{modules/1-E/readiness/outcomes.tex}
\input{modules/1-E/readiness/resources.tex}


\CatchFileDef{\activities}{modules/1-E/activities.tex}{}



\newModuleSection
\begin{goals}
In this module, we will learn how to solve all systems of equations. Today, we will learn how to write the solution sets using set builder notation.
\end{goals}
\includeActivities{1}{10}{\activities}
\begin{summary}
Today we learned how to write the solution sets of systems of equations using set builder notation.
\end{summary}

\newModuleSection
\begin{goals}
Today we will learn
\begin{itemize}
\item How to represent systems of equations in different ways (Standard E1)
\item How to use (augmented) matrices to turn a complicated system into a simpler system so we can describe the solution set (Standard E2).
\end{itemize}
\end{goals}
\includeActivities{11}{20}{\activities}
\begin{summary}
Today we learned
\begin{itemize}
\item How to represent systems of equations in different ways (Standard E1)
\item How to use (augmented) matrices to turn a complicated system into a simpler system so we can describe the solution set (Standard E2).
\end{itemize}
\vfill
Next class we will learn how to put a matrix in reduced row echelon form (Standard E2).
\end{summary}

\newModuleSection
\begin{goals}
Today we will learn how to put a matrix in reduced row echelon form (Standard E2).
\end{goals}
\includeActivities{21}{30}{\activities}
\begin{summary}
Today we learned how to put a matrix in reduced row echelon form (Standard E2).
\end{summary}

\newModuleSection
\begin{goals}
Today we will learn
\begin{itemize}
\item How to write the solution set of a linear system when there are infinitely many solutions
\item How to put together everything we have learned to solve any system of linear equations.
\end{itemize}
\end{goals}
\includeActivities{31}{37}{\activities}
\begin{summary}
Today we put together everything we have learned previously and learned how to solve any system of linear equations.
\end{summary}



\end{module}
