\begin{problem}{V5}
Determine if the set of all lattice points, i.e. \(\{(x,y)\ \big|\ \text{\(x\) and \(y\) are integers} \}\) is a subspace of \(\IR^2\).
\end{problem}
\begin{solution}
This set is closed under addition, but not under scalar multiplication so it is not a subspace.
\end{solution}

\begin{problem}{V5}
Determine if \(\left\{ \begin{bmatrix} x \\ y \\ 0 \\ z \end{bmatrix}\  \bigg|\ x,y,z \in \IR\right\}\)  a subspace of \(\IR^4\).
\end{problem}
\begin{solution}
It is closed under addition and scalar multiplication, so it is a subspace.  Alternatively, it is the image of the linear transformation from \(\IR^3 \rightarrow \IR^4\) given by \[\begin{bmatrix} x \\ y \\ z \end{bmatrix} \mapsto  \begin{bmatrix} x \\ y \\ 0 \\ z \end{bmatrix}.\]
\end{solution}


\begin{problem}{V5} Let \(W\) be the set of all polynomials of even degree.  Determine if \(W\) is a subspace of the vector space of all polynomials.
\end{problem}
\begin{solution}
\(W\) is closed under scalar multiplication, but not under addition.  For example, \(x-x^2\) and \(x^2\) are both in \(W\), but \((x-x^2)+(x^2)=x \notin W\).
\end{solution}


\begin{problem}{V5} Let \(W\) be the set of all polynomials of the form
\(ax^3+bx\).  Determine if \(W\) is a subspace of \(\P^3\).
\end{problem}
\begin{solution}
Yes because \(s(a_1x^3+b_1x)+t(a_2x^3+b_2x)=
(sa_1+ta_2)x^3+(sb_1+tb_2)x\) also belongs to \(W\).
Alternately, yes because \(W\) is isomorphic to \(\IR^2\).
\end{solution}


\begin{problem}{V5} Let \(W\) be the set of all \(\IR^3\) vectors
\(\begin{bmatrix} x \\ y \\ z \end{bmatrix}\)
satisfying \(x+y+z=1\) (this forms a plane).
Determine if \(W\) is a subspace of \(\IR^3\).
\end{problem}
\begin{solution}
No, because \(\mathbf{0}\) does not belong to \(W\).
\end{solution}


\begin{problem}{V5} Let \(W= \setBuilder{\begin{bmatrix} x \\ y \\ z \end{bmatrix}}{x+y+z=0}\) (this forms a plane).
Determine if \(W\) is a subspace of \(\IR^3\).
\end{problem}
\begin{solution}
Yes, because \(z=-x-y\) and
\(
  a\begin{bmatrix} x_1 \\ y_1 \\ -x_1-y_1 \end{bmatrix}+
  b\begin{bmatrix} x_2 \\ y_2 \\ -x_2-y_2 \end{bmatrix}=
  \begin{bmatrix}
    ax_1+bx_2 \\
    ay_1+by_2 \\
    -(ax_1+bx_2)-(ay_1+by_2)
  \end{bmatrix}
\).
Alternately, yes because \(W\) is isomorphic to \(\IR^2\).
\end{solution}

\begin{problem}{V5} Let \(W= \setBuilder{\begin{bmatrix} x \\ y \\ z \end{bmatrix}}{x+y=3z}\) (this forms a plane).
Determine if \(W\) is a subspace of \(\IR^3\).
\end{problem}
\begin{solution}
Yes.
\end{solution}

\begin{problem}{V5} Let \(W= \setBuilder{\begin{bmatrix} x \\ y \\ z \end{bmatrix}}{x+y=3}\) (this forms a plane).
Determine if \(W\) is a subspace of \(\IR^3\).
\end{problem}
\begin{solution}
No.
\end{solution}

\begin{problem}{V5} Let \(W\) be the set of all complex numbers
that are purely real (i.e of the form \(a+0i\))  or purely imaginary (i.e. of the form \(0+bi\)).
Determine if \(W\) is a subspace of \(\IC\).
\end{problem}
\begin{solution}
No, because \(1\) is purely real and \(i\) is purely imaginary, but
the linear combination \(1+i\) is neither.
\end{solution}


\begin{problem}{V5} Let \(W\) be the set of all complex numbers \(a+bi\)
satisfying  \(a=2b\).
Determine if \(W\) is a subspace of \(\IC\).
\end{problem}
\begin{solution}
Yes, because \(c(2b_1+b_1i)+d(2b_2+b_2i)=2(cb_1+db_2)+(cb_1+db_2)i\) belongs to
\(W\). Alternately, yes because \(W\) is isomorphic to \(\IR\).
\end{solution}
