%!TEX root =../../course-notes.tex
% ^ leave for LaTeXTools build functionality

\begin{applicationActivities}{4}{28}
\begin{observation}
Recall from last class:
\begin{itemize}
\item To find eigenvalues the eigenvalues of a matrix $A$, we need to find values of $\lambda$ such that $A-\lambda I$ has a nontrivial kernel; equivalently, $A-\lambda I$ is not invertible, which is equivalent to $\det(A-\lambda I)=0$.  
\item $\det(A-\lambda I)$ is called the \term{characteristic polynomial} of $A$.  It is a polynomial in the variable $\lambda$.
\item Once an eigenvalue is found, the eigenvectors form a subspace called the \term{eigenspace}, which is simply the kernel of $A-\lambda I$.  Each eigenvalue will have an associated eigenspace.
\end{itemize}
\end{observation}

\begin{activity}{5}
  If $A$ is a $4 \times 4$ matrix, what is the largest number of eigenvalues $A$ can have?
  \begin{enumerate}[(a)]
  \item $3$
  \item $4$
  \item $5$
  \item $6$
  \item It can have infinitely many
  \end{enumerate}
\end{activity}

\begin{activity}{10}
  $2$ is an eigenvalue of each of the matrices $A=\begin{bmatrix} 1 & -2 & 1 \\ -1 & 0 & 1 \\ -1 & -2 & 3\end{bmatrix}$ and $B=\begin{bmatrix} -3 & -9 & 5 \\ -2 & -2 & 2 \\ -7 & -13 & 9 \end{bmatrix}$.

  Compute the eigenspace associated to $2$ for both $A$ and $B$.
\end{activity}

\begin{definition}

\begin{itemize}
\item The \term{algebraic multiplicity} of an eigenvalue is its multiplicity as a root of the characteristic polynomial.
\item The \term{geometric multiplicity} of an eigenvalue is the dimension of the eigenspace.
\end{itemize}

\end{definition}

\begin{activity}{5} How are the algebraic and geometric multiplicities related?
\begin{enumerate}[(a)]
\item The algebraic multiplicity is always at least as big as than the geometric multiplicity.
\item The geometric multiplicity is always at least as big as the algebraic multiplicity.
\item Sometimes the algebraic multiplicity is larger and sometimes the geometric multiplicity is larger.
\end{enumerate}
\end{activity}

\begin{activity}{20}
   Find all of the eigenvalues, along with both their algebraic and geometric multiplicities, for the matrix $\begin{bmatrix} -3 & 1 & 2 & 1 \\ -9 & 5 & -2 & -1 \\ 31 & -17 & 6 & 3 \\ -69 & 39 & -18 & -9 \end{bmatrix}$.  Use technology to help you!
\end{activity}



\begin{activity}{10}
Let  $A=\begin{bmatrix}0 & -1 \\ 1 & 0 \end{bmatrix}$.
\begin{subactivity}
  Find the eigenvalues of $A$
  \end{subactivity}
  \begin{subactivity}
   Describe what this linear transformation is doing geometrically; draw a picture.
   \end{subactivity}
\end{activity}



\end{applicationActivities}
