%!TEX root =../../course-notes.tex
% ^ leave for LaTeXTools build functionality

\begin{applicationActivities}{3}{19}
\begin{activity}{10}
  \begin{subactivity}
    Describe surjective linear transformations in terms of the image.
  \end{subactivity}
  \begin{subactivity}
    Describe injective linear transformations in terms of the kernel.
  \end{subactivity}
\end{activity}

\begin{activity}{15}
Let $T: \IR^n \rightarrow \IR^m$ be a linear map with matrix $A \in M_{m,n}$ (for the standard basis).  You have cards containing a number of statements about $T$ and $A$.  Sort them into groups of equivalent statements, and post them on your board.

\begin{TBLnote}Card sort activity for 10-15 minutes: cards contain the following
\begin{enumerate}[(a)]
\item $T$ is injective
\item $T$ is not injective
\item $T$ is surjective
\item $T$ is not surjective
\item The system of linear equations given by the augmented matrix $\begin{bmatrix}[c|c]A & \vec{b} \end{bmatrix}$ has a solution for all $\vec{b} \in \IR^m$
\item The system of linear equations given by the augmented matrix $\begin{bmatrix}[c|c]A & \vec{b} \end{bmatrix}$ has a unique solution for all $\vec{b} \in \IR^m$
\item The system of linear equations given by the augmented matrix $\begin{bmatrix}[c|c] A & \vec{0} \end{bmatrix}$ has a non-trivial solution.
\item The columns of $A$ span $\IR^m$
\item The columns of $A$ are linearly independent
\item The columns of $A$ are a basis of $\IR^m$
\item Every column of $\RREF(A)$ is a pivot column
\item $\RREF(A)$ has a non-pivot column
\item $\RREF(A)$ has $n$ pivot columns
\end{enumerate}
\end{TBLnote}
\end{activity}

\begin{activity}{25}
\begin{TBLnote}Gallery walk --3 minutes per board.  Then 10 minutes to wrap up discussion \end{TBLnote}
Cycle around the room counter-clockwise.  If they have two things grouped together that you know are not equivalent, write a reason or counter-example on a sticky note.
\end{activity}


\end{applicationActivities}
